---
title: "TriCoMM R Notebook"
author: "Sam Pell"
output: html_notebook
---

***TriCoMM Workbook*** *Sam Pell, Jane Corah, and Alex Miroshnichenko*

```{r}
df = read.csv(url("https://raw.githubusercontent.com/samplle/TriCoMM/main/TriCoMM_DNC_data.csv"))
df = df[,-1]

df$AvgReduxinNighttimeAnnualTemp_Fahrenheit = df$AvgReduxinNighttimeAnnualTemp_Celsius * (9/5)
df = df[,-1]
df = df[,c(5,1:4)]

head(df, 8)
```

Above, we load in the data set, using the read.csv() command, and store it as data frame df. Then, we remove the first column, which only contains a constant value that appears to be unimportant. Finally, we present a head of the data, which allows us to see how the data is formatted, and what values we are working with.

```{r}
poverty_mod = lm(AvgReduxinNighttimeAnnualTemp_Fahrenheit ~ PercentPopIncomeBelow2xPovertyLevel, data = df)
greenspace_mod <- lm(AvgReduxinNighttimeAnnualTemp_Fahrenheit ~ Percent_GreenSpace, data = df)
poverty_greenspace_mod <- lm(Percent_GreenSpace ~ PercentPopIncomeBelow2xPovertyLevel, data = df)

plot(AvgReduxinNighttimeAnnualTemp_Fahrenheit ~ PercentPopIncomeBelow2xPovertyLevel, data = df)

abline(poverty_mod, col = 'blue2', lw = 2)

plot(AvgReduxinNighttimeAnnualTemp_Fahrenheit ~ Percent_GreenSpace, data = df)

abline(greenspace_mod, col = 'coral', lw = 2)

plot(Percent_GreenSpace ~ PercentPopIncomeBelow2xPovertyLevel, data = df)

abline(poverty_greenspace_mod, col = 'green2', lw = 2)
```

```{r}
plot(poverty_mod)
plot(greenspace_mod)
plot(poverty_greenspace_mod)
anova(poverty_mod, greenspace_mod)

summary(poverty_mod)
summary(greenspace_mod)
summary(poverty_greenspace_mod)
```

```{r}
loc_mod <- lm(AvgReduxinNighttimeAnnualTemp_Fahrenheit ~ long+lat, data = df)
plot(loc_mod)
anova(mod1, loc_mod)
```

```{r}
ggplot(df, aes(long, lat, color = Percent_GreenSpace)) +
  geom_point(alpha = 0.6, size = 3.5) +
  scale_color_gradient("% Greenspace", low = "#FFFFFF", high = "#004400")

ggplot(df, aes(long, lat, color = AvgReduxinNighttimeAnnualTemp_Fahrenheit)) +
  geom_point(alpha = 0.6, size = 3.5) + 
  scale_color_gradient("Avg Annual Night Redux in Temp (F)", low = "#FF0000", high = "#0000FF")

ggplot(df, aes(long, lat, color = PercentPopIncomeBelow2xPovertyLevel)) +
  geom_point(alpha = 0.9, size = 3.5) +
  scale_color_gradient("% of Pop Below 2x Poverty Rate", low = "#7851A9", high = "#FFFF00")
```

```{r}
ggplot(df, aes(long, lat, color = AvgReduxinNighttimeAnnualTemp_Fahrenheit)) +
  geom_point(alpha = 0.6, size = 3.5) + 
  scale_color_gradient("Avg Annual Night Redux in Temp (C)", low = "#FF0000", high = "#0000FF") +
  geom_point(mapping = aes(long, lat, color = PercentPopIncomeBelow2xPovertyLevel))
```

```{r}
poverty_above_50 <- df[df$PercentPopIncomeBelow2xPovertyLevel >= 50,]
poverty_below_50 <- df[df$PercentPopIncomeBelow2xPovertyLevel < 50,]
redux_above_mean <- df[df$AvgReduxinNighttimeAnnualTemp_Fahrenheit >= mean(df$AvgReduxinNighttimeAnnualTemp_Fahrenheit),]

mean(poverty_above_50$AvgReduxinNighttimeAnnualTemp_Fahrenheit)
mean(poverty_below_50$AvgReduxinNighttimeAnnualTemp_Fahrenheit)

t.test(poverty_above_50$AvgReduxinNighttimeAnnualTemp_Fahrenheit, poverty_below_50$AvgReduxinNighttimeAnnualTemp_Fahrenheit)

mean(poverty_above_50$Percent_GreenSpace)
mean(poverty_below_50$Percent_GreenSpace)

t.test(poverty_above_50$Percent_GreenSpace, poverty_below_50$Percent_GreenSpace)
```

```{r}
ggplot(poverty_above_50, aes(long, lat, color = Percent_GreenSpace)) +
  geom_point(alpha = 1, size = 3.5) +
  scale_color_gradient("% Greenspace", low = "#FFFFFF", high = "#004400")

ggplot(poverty_below_50, aes(long, lat, color = Percent_GreenSpace)) +
  geom_point(alpha = 1, size = 3.5) +
  scale_color_gradient("% Greenspace", low = "#FFFFFF", high = "#004400")
```

```{r}
ggplot(poverty_above_50, aes(long, lat, color = AvgReduxinNighttimeAnnualTemp_Fahrenheit)) +
  geom_point(alpha = 1, size = 3.5) +
  scale_color_gradient("Avg Annual Night Redux in Temp (F)", low = "#FF0000", high = "#0000FF")

ggplot(poverty_below_50, aes(long, lat, color = AvgReduxinNighttimeAnnualTemp_Fahrenheit)) +
  geom_point(alpha = 1, size = 3.5) +
  scale_color_gradient("Avg Annual Night Redux in Temp (F)", low = "#FF0000", high = "#0000FF")
```

```{r}
target_areas <- df[(df$long >= -79.1 & df$long <= -79.05 & df$lat >= 35.9 & df$lat <= 35.925) | (df$long >= -78.95 & df$long <= -78.85 & df$lat >= 35.975 & df$lat <= 36.025),]
  
#  long (-79.1<=x<=-79.05), lat (35.9<=x<=35.925), 
#  long (-78.95<=x<=-78.85), lat(35.975<=x<=36.025)

ggplot(target_areas, aes(long, lat, color = Percent_GreenSpace)) +
  geom_point(alpha = 0.6, size = 3.5) +
  scale_color_gradient("% Greenspace", low = "#FFFFFF", high = "#004400")
```

```{r}
t.test(target_areas$Percent_GreenSpace, df$Percent_GreenSpace)

t.test(target_areas$PercentPopIncomeBelow2xPovertyLevel, df$PercentPopIncomeBelow2xPovertyLevel)


t.test(target_areas$AvgReduxinNighttimeAnnualTemp_Fahrenheit, df$AvgReduxinNighttimeAnnualTemp_Fahrenheit)
```
